---
title: "Lab 01 - Hello R"
author: "Rowan Kemmerly"
date: "1.23.23"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

It has 13 rows and 6 columns. The variables included are "dataset", "mean_x", "mean_y", std_dev_x", "std_dev_y", and "corr_x_y".

### Exercise 2

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Even though this plot of the star dataset looks very different than the code of the dino dataset...

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

...the correlation coefficients between x and y for both datasets are the same!

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

Plotting the "circle" dataset, we can see that again, these data appear quite visually dissimilar to the dino data. 

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

But the the correlation coefficient between x and y for this dataset is only marginally lower than the correlation coefficient for the dino dataset! (They are basically the same, almost certainly not statistically different from one another.)

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

Add code and narrative as needed.

To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.




